---
title: "Senior Project"
author: "Carlos Rodriguez-Munoz"
date: "1/25/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{css echo=FALSE}
pre {
  margin-left: 40px;
}
div.sourceCode {
  margin-left: 40px;
}
div.solution {
  margin-left: 40px;
  border: 1px dashed red;
  padding: 2px;
}
span.solution { display: block; }
li { margin-top: 20px; }
li li { margin-top: 2px; }
```
```{solution,eval=FALSE}
.,.,.
```
Packages and Libraries

```{r}
#install.packages("deSolve")
library(deSolve)
#install.packages("plot3D")
library("plot3D")
#install.packages("ggplot2")
library(ggplot2)
#install.packages("rgl")
#install.packages("manipulate")
library(manipulate)
#install.packages("rootSolve")
#install.packages("plotly")
library(plotly)
library(rootSolve)
#install.packages("numDeriv")
library(numDeriv)
#install.packages("cOde")
library(cOde)
#install.packages("phaseR")
library(phaseR)
#install.packages("plot3D")
#install.packages("rgl")
library(plot3D)
library(rgl)
#install.packages("scatterplot3d")
```

We can begin by first defining some variables and parameters as stated in the paper:

$$state: {I = 0.069, A = 0.458, D= 0.473}$$

```{r}

state <- c(I = 0.069, A = 0.458, D = 0.473)

parameters <- c(beta1 = 0.4842, beta2 = 0.5776, alpha1 = 0.7439, alpha2 = 0.2990, gamma1 = 0.4498, gamma2 = 0.1699)


```


Next, we will build the model

$$ i^\prime = -\beta_1 ai - \beta_2 di + \gamma_1a + \gamma_2d, \\
a^\prime = \beta_1 ai + \alpha_1 ad - \alpha_2 ad - \gamma_1 a, \\
d^\prime = \beta_2 ai + \alpha_2 ad - \alpha_1 ad - \gamma_2 d$$

```{r}
IAD <- function(t, state, parameters) {
  with(as.list(c(state,parameters)), {
    dI <- -(beta1 * A * I) - (beta2 * D * I ) + (gamma1 * A) + (gamma2 * D)
    dA <- (beta1 * A * I) + (alpha1 * A * D ) - (alpha2 * A * D ) - (gamma1 * A)
    dD <- (beta2 * D * I) - (alpha1 * A * D ) + (alpha2 * A * D ) - (gamma2 * D)
    list(c(dI,dA,dD))
  })
}

```

Specify the time and intervals

```{r}
time.max <- 300
time.max.1 <- time.max + 1
time.min <- 0
time.min.1 <- time.min + 1
times <- seq(time.min, time.max, by = 1)

```

Solve the ODE with given parameters:

```{r}

out <- ode(y = state, times = times, func = IAD, parms = parameters)
head(out)
out.df <- as.data.frame(out)
```


Lots of data on Trump Approval, going to break it up into pieces to make more manageable and scale them down 100 so make it more continuous for the ODE

```{r}
trump.approval <- read.csv("https://projects.fivethirtyeight.com/trump-approval-data/approval_polllist.csv")

#Gallup Polls
gallup.trump.approval <- trump.approval[trump.approval$pollster=="Gallup",c("approve", "disapprove")]
colnames(gallup.trump.approval) <-  c("agree", "disagree")
length.gallup <- length(gallup.trump.approval[,"agree"])
rownames(gallup.trump.approval) <-  c(1:length.gallup)
gallup.trump.approval <-  gallup.trump.approval[-c(859),]
gallup.trump.approval[,"agree"] <- gallup.trump.approval[,"agree"]/100
gallup.trump.approval[,"disagree"] <- gallup.trump.approval[,"disagree"]/100
gallup.trump.approval$indifferent <- 1 - gallup.trump.approval$agree - gallup.trump.approval$disagree
gallup.trump.approval$time <- c(0:857)
gallup.trump.approval <- gallup.trump.approval[1:429,]

#Morning Consult
mc.trump.approval <- trump.approval[trump.approval$pollster=="Morning Consult",c("approve", "disapprove")]
colnames(mc.trump.approval) <- c("agree","disagree")
length.mc <- length(mc.trump.approval[,"agree"])
rownames(mc.trump.approval) = c(1:length.mc)
mc.trump.approval[,"agree"] <- mc.trump.approval[,"agree"]/100
mc.trump.approval[,"disagree"] <- mc.trump.approval[,"disagree"]/100
mc.trump.approval$indifferent <- 1 - mc.trump.approval$agree - mc.trump.approval$disagree


```



Graph of the paper's model and parameters as compared to the real data

```{r}
f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#000"
)

l <- list(
  font = list(
    family = "sans-serif",
    size = 12,
    color = "#000"),
  bgcolor = "#E2E2E2",
  bordercolor = "#FFFFFF",
  borderwidth = 2)

x.title <- list(
  title = "Time (About Semi-Weekly)",
  titlefont = f#,
  #range = c(0, 800)
)

y.title <- list(
  title = "Percent of Population",
  titlefont = f,
  range = c(0, 0.65)
)

t <- list(
  family = "Courier New, monospace",
  size = 15,
  color = "#000"
)

time.series <- plot_ly(out.df, x = times, y = out.df$I, type = "scatter", mode = "lines", name  = "Indifferent")
time.series <- time.series %>% add_trace(y = out.df$A, name = "Agree")
time.series <- time.series %>% add_trace(y = out.df$D, name = "Disagree")
time.series <- time.series %>% layout(title = "Model Time Series of I, A, D", xaxis = x.title, yaxis = y.title, legend= c(l, list(title=list(text='<b> Populations </b>'))))
time.series

time.series.2 <- plot_ly(gallup.trump.approval, x = gallup.trump.approval$time, y = gallup.trump.approval$indifferent, name = "IndifferentR", type = "scatter", mode = "markers")
time.series.2 <- time.series.2 %>% add_trace(y = gallup.trump.approval$agree , name = "AgreeR")
time.series.2 <- time.series.2 %>% add_trace(y = gallup.trump.approval$disagree, name = "DisagreeR")
time.series.2 <- time.series.2 %>% layout(title = "Real Gallup Data", font = t, xaxis = x.title, yaxis = y.title, legend= c(l, list(title=list(text='<b> Populations </b>'))))
time.series.2

#, autosize = F, width = 1200, height = 800
```


Graph ODES onto One 3D Graph

```{r}
#z = as.matrix(c(1,0,0,0,1,0, 0,0,1), nrow = 3, ncol = 3,byrow = FALSE)
ode.3d.graph <- plot_ly(out.df, x = out.df$I, y = out.df$A, z = out.df$D, type = 'scatter3d', mode = 'lines', opacity = 1, line = list(width = 6, color = "blue", reverscale = FALSE), name = "Relationship between Indifferent, Agree, and Disagree over Time")
ode.3d.graph <- ode.3d.graph %>% layout(
    title = "Relationship between I, A, and D",
    scene = list(
      xaxis = list(title = "Indifferent", font = f),
      yaxis = list(title = "Agree", font = f),
      zaxis = list(title = "Disagree", font = f)
    ))
#ode.3d.graph <- ode.3d.graph %>% add_surface(z)

ode.3d.graph

```



Initial Conditions for the various polling

```{r}
#gallup.trump.approval <- gallup.trump.approval[1:429,]

state.gallup <- c(I = gallup.trump.approval[time.min.1,"indifferent"], A = gallup.trump.approval[time.min.1,"agree"], D = gallup.trump.approval[time.min.1,"disagree"])
state.gallup

```

```{r}
#Sets the populations to be tested against
Indifferent.gallup <- gallup.trump.approval[time.min.1:time.max.1,"indifferent"]
Agree.gallup <- gallup.trump.approval[time.min.1:time.max.1,"agree"]
Disagree.gallup <- gallup.trump.approval[time.min.1:time.max.1,"disagree"]

#Function tests the data from the ODE with the real data
RSS <- function(parameters) {
  names(parameters) <- c("beta1", "alpha1", "alpha2", "gamma1" ,"beta2", "gamma2")
  out.fit <- as.data.frame(ode(y = state.gallup, times = times, func = IAD, parms = parameters))
  out.fit <- out.fit[,c(2,3,4)]
  sum((Disagree.gallup-out.fit[,3])^2 + (Indifferent.gallup-out.fit[,1])^2 + (Agree.gallup - out.fit[,2])^2)
}

#Function that adjusts the parameters to better fit the data
Opt <- optim(c(0.2497, 0.5234,0.5433,0.01,0.8999,0.01), RSS, method = "L-BFGS-B" , upper = c(1, 1), lower = c(0, 0)) 

#Assigns names to the parameters
Opt_par <- setNames(Opt$par, c("beta1", "alpha1", "alpha2", "gamma1" ,"beta2", "gamma2"))
Opt_par

#Fitting ODE
out.fit <- as.data.frame(ode(y = state.gallup, times = times, func = IAD, parms = Opt_par))
out.fit <- out.fit[,c(2,3,4)]
#300   c(0.5, 0.5,0.5,0.5,0.5,0.5) c(0.2497, 0.5234,0.5433,0.01,0.8999,0.01)
```

```{r}
parameters.2 <- c(beta1 = as.numeric(Opt_par[1]), beta2 = as.numeric(Opt_par[5]), alpha1 = as.numeric(Opt_par[2]), alpha2 = as.numeric(Opt_par[3]), gamma1 = as.numeric(Opt_par[4]), gamma2 = as.numeric(Opt_par[6]))

out.2 <- ode(y = state.gallup, times = times, func = IAD, parms = parameters.2)
head(out.2)
out.2.df <- as.data.frame(out.2)
parameters.2
```

```{r}

sum((Agree.gallup - out.2.df[,"A"])^2 + (Indifferent.gallup - out.2.df[,"I"])^2 + (Disagree.gallup - out.2.df[,"D"])^2)
parameters.2

```

```{r}

time.series <- plot_ly(out.2.df, x = times, y = out.2.df$I, type = "scatter", mode = "lines", name  = "Indifferent")
time.series <- time.series %>% add_trace(y = out.2.df$A, name = "Agree")
time.series <- time.series %>% add_trace(y = out.2.df$D, name = "Disagree")
time.series <- time.series %>% layout(title = "Model Time Series of I, A, D", xaxis = x.title, yaxis = y.title, legend= c(l, list(title=list(text='<b> Populations </b>'))))
time.series

time.series.2 <- plot_ly(gallup.trump.approval, x = gallup.trump.approval$time, y = gallup.trump.approval$indifferent, name = "IndifferentR", type = "scatter", mode = "markers")
time.series.2 <- time.series.2 %>% add_trace(y = gallup.trump.approval$agree , name = "AgreeR")
time.series.2 <- time.series.2 %>% add_trace(y = gallup.trump.approval$disagree, name = "DisagreeR")
time.series.2 <- time.series.2 %>% layout(autosize = F, width = 1200, height = 400, title = " Real Gallup Data", xaxis = x.title, yaxis = y.title, legend= c(l, list(title=list(text='<b> Populations </b>'))))
time.series.2



```


```{r}
if (!require("processx")) install.packages("processx")
orca(time.series.2, "Real Gallup Data.png")
```


Symbolically Solve the Jacobian

```{r}

J.norm <- jacobianSymb(c(I.prime = "-beta1 * A * I - beta2 * D * I  + gamma1 * A + gamma2 * D", A.prime = "beta1 * A * I + alpha1 * A * D  - alpha2 * A * D  - gamma1 * A", D.prime = "beta2 * D * I - alpha1 * A * D  + alpha2 * A * D  - gamma2 * D"), c("I","A","D"))


J.norm

```

```{r}
state.3 <- c(I = 0.1, A = 0.45, D = 0.45)
parameters.3 <- parameters.2
times.3 <- seq(0, 10000, by = 1)

out.long <- ode(y = state.3, times = times.3, func = IAD, parms = parameters.3)
out.long.df <- as.data.frame(out.long)

```

```{r}
tail <- tail(out.long.df,n=1)
tail
```


Numerically solve Jacobian based on our parameters and ODE

```{r}
time.jac <- 300
Jacobian <- matrix(nrow = 3, ncol=3)
beta1 <- as.numeric(parameters.2[1])
beta2 <- as.numeric(parameters.2[2])
alpha1 <- as.numeric(parameters.2[3])
alpha2 <- as.numeric(parameters.2[4])
gamma1 <- as.numeric(parameters.2[5])
gamma2 <- as.numeric(parameters.2[6])
i.jac <-  tail$I
a.jac <-  tail$A
d.jac <-  tail$D

Jacobian[1,1] <- -beta1 * a.jac - beta2 * d.jac
Jacobian[1,2] <- gamma1 - beta1 * i.jac
Jacobian[1,3] <- gamma2 - beta2 * i.jac
Jacobian[2,1] <- beta1 * a.jac   
Jacobian[2,2] <- beta1 * i.jac + alpha1 * d.jac - alpha2 * d.jac - gamma1
Jacobian[2,3] <- alpha1 * a.jac - alpha2 * a.jac
Jacobian[3,1] <- beta2 * d.jac
Jacobian[3,2] <- alpha2 * d.jac - alpha1 * d.jac
Jacobian[3,3] <- beta2 * i.jac - alpha1 * a.jac + alpha2 * a.jac - gamma2
  
Jacobian  
det(Jacobian)
eigen(Jacobian)$values
```

Edge Testing
This creates a data frame with different initial conditions

```{r}
sequence.ict <- seq(0,1, by = 0.05)
states.df <- c()
for(i in sequence.ict) {
  for(a in sequence.ict) {
    for(d in sequence.ict) {
      states.df <- rbind(states.df, c(i,a,d))
    }
  }
}
states.df <- as.data.frame(states.df)
colnames(states.df) <- c("initial.I", "initial.A", "initial.D")
states.df <- rbind(states.df, c(as.numeric(state.gallup[1]),as.numeric(state.gallup[2]),as.numeric(state.gallup[3])))
states.df$Sum <- states.df$initial.I + states.df$initial.A + states.df$initial.D
states.df <- states.df[states.df$Sum == 1,]
rownames(states.df) <- 1:length(states.df[,"initial.I"])
triples.df <- states.df
```

Now we want to run the ODE solver with the different initial conditions and get the equilibria. 

```{r}
equilibria.df <- c()
for(i in 1:length(states.df[,"initial.I"])) {
  out.ict <- ode(y = c(I = as.numeric(states.df[i,1]), A = as.numeric(states.df[i,2]), D = as.numeric(states.df[i,3])), times = times, func = IAD, parms = parameters.2)
  out.ict.df <- as.data.frame(out.ict)
  equilibria.df <- rbind(equilibria.df,out.ict.df[time.max,c("I","A","D")])
}
length(states.df[,"initial.I"])
```

Cleaning the equilibria dataframe and adding the initial conditions to make better sense of it.

```{r}
row.names(equilibria.df) <- 1:length(equilibria.df[,1])
colnames(equilibria.df) <- c("equilibrium.I", "equilibrium.A", "equilibrium.D")
equilibria.df <- cbind(equilibria.df,states.df[,c("initial.I", "initial.A", "initial.D")])

```

Establishes a distance from the equilibrium point of the actual initial condition problem

```{r}
equilibria.df$Distance <- ((equilibria.df$equilibrium.I - equilibria.df[length(equilibria.df[,1]),"equilibrium.I"])^2 + (equilibria.df$equilibrium.A - equilibria.df[length(equilibria.df[,1]),"equilibrium.A"])^2 + (equilibria.df$equilibrium.D - equilibria.df[length(equilibria.df[,1]),"equilibrium.D"])^2)

```

We then sort the data by ascending distance
```{r}
equilibria.df <- equilibria.df[order(equilibria.df$Distance),]
row.names(equilibria.df) <- 1:length(equilibria.df[,1])
```

Test a graph for a row in the equilibria data frame

```{r}
row <- 154
#state.test <- c(I = as.numeric(equilibria.df[row,"initial.I"]), A = as.numeric(equilibria.df[row,"initial.A"]), D = as.numeric(equilibria.df[row,"initial.D"]))
times.1 <- seq(0,800,1)
state.test <- c(I = 0.1, A = 0.45, D = 0.45)
out.test <- ode(y = state.test, times = times.1, func = IAD, parms = parameters.2)
out.test <- as.data.frame(out.test)
test.time.series <- plot_ly(out.test, x = times.1, y = out.test$I, type = "scatter", mode = "lines", name  = "Indifferent")
test.time.series <- test.time.series %>% add_trace(y = out.test$A, name = "Agree")
test.time.series <- test.time.series %>% add_trace(y = out.test$D, name = "Disagree")
test.time.series <- test.time.series %>% layout(title = paste("Model Estimation given I(0)=", state.test[1], "A(0)=", state.test[2], "D(0)= ", state.test[3]), xaxis = x.title, yaxis = y.title, legend= c(l, list(title=list(text='<b> Populations </b>'))))
test.time.series
#,autosize = F, width = 1200, height = 800
```

```{r}
J.i0 <- jacobianSymb(c(I.prime = "-beta1 * A * 0- beta2 * D * 0  + gamma1 * A + gamma2 * D", A.prime = "beta1 * A * 0 + alpha1 * A * D  - alpha2 * A * D  - gamma1 * A", D.prime = "beta2 * D * 0 - alpha1 * A * D  + alpha2 * A * D  - gamma2 * D"), c("I","A","D"))

J.a0 <- jacobianSymb(c(I.prime = "-beta1 * 0 * I - beta2 * D * I  + gamma1 * 0 + gamma2 * D", A.prime = "beta1 * 0 * I + alpha1 * 0 * D  - alpha2 * 0 * D  - gamma1 * 0", D.prime = "beta2 * D * I - alpha1 * 0 * D  + alpha2 * 0 * D  - gamma2 * D"), c("I","A","D"))

J.d0 <- jacobianSymb(c(I.prime = "-beta1 * A * I - beta2 * 0 * I  + gamma1 * A + gamma2 * 0", A.prime = "beta1 * A * I + alpha1 * A * 0  - alpha2 * A * 0  - gamma1 * A", D.prime = "beta2 * 0 * I - alpha1 * A * 0  + alpha2 * A * 0  - gamma2 * 0"), c("I","A","D"))

J.a0
```




```{r}
c(gamma1 / beta1, 1-gamma1 / beta1)
c(gamma2 / beta2,1-gamma2 / beta2)
```


```{r}
ID <- function(t, state = state.gallup, parameters = parameters.2) {
  with(as.list(c(state,parameters)), {
    dx <- -beta2 * x * y  + gamma2 * y
    dy <- beta2 * x * y - gamma2 * y
    list(c(dx,dy))
  })
}


ID_flowField <- flowField(ID, xlim   = c(-0.05, 1), ylim   = c(0, 1), points = 17, add = FALSE, xlab = "i", ylab = "d")
abline(v = 0, col = "black")
ID_nullclines  <- nullclines(ID, xlim   = c(-0.5, 1), ylim   = c(-0.5, 1),  points = 200, col = c("pink","blue"), add.legend = FALSE)
abline(a = 1, b = -1, col = "green")
#ID_trajectory  <- trajectory(ID, y0   = y0, tlim = c(0, 10))
points(x = gamma2 / beta2, y = 1 - gamma2 / beta2, pch = 19)
text(x = gamma2 / beta2, y = 1 - gamma2 / beta2, labels = c(paste("(",round(gamma2 / beta2,4), ",", 1 - round(gamma2 / beta2,4),")")))
```

```{r}
IA <- function(t, state = state.gallup, parameters = parameters.2) {
  with(as.list(c(state,parameters)), {
    dx <- -beta1 * x * y  + gamma1 * y
    dy <- beta1 * x * y - gamma1 * y
    list(c(dx,dy))
  })
}

IA_flowField <- flowField(IA, xlim   = c(0, 1), ylim   = c(0, 1), points = 17, add = FALSE, xlab = "i", ylab = "a")
abline(v = 0, col = "black")
y0 <- matrix(c(0.03, 0.97, 0.3, 0.7,0.9, 0.1, 0.7, 0.3), 4, 2, byrow = TRUE)
IA_nullclines  <- nullclines(IA, xlim   = c(-0.5, 1), ylim   = c(-0.5, 1),  points = 200, col = c("pink","blue"), add.legend = FALSE)
abline(a = 1, b = -1, col = "green")
#ID_trajectory  <- trajectory(ID, y0   = y0, tlim = c(0, 10))
points(x = gamma1 / beta1, y = 1 - gamma1 / beta1, pch = 19)
text(x = gamma1 / beta1, y = 1 - gamma1 / beta1, labels = c(paste("(",round(gamma1 / beta1,4), ",", 1 - round(gamma1 / beta1,4),")")))
```



```{r}
parameters.2
tail
Jacobian
det(Jacobian)
eigen(Jacobian)$values
```

```{r}
```


```{r}
```




```{r}
x <- out.2.df$I
y <- out.2.df$A
z <- out.2.df$D

#rglwidget() # Open a new RGL device
#rgl.bg(color = "white")
#rgl.points(x = out.2.df$I, y = out.2.df$A, z = out.2.df$D) # Scatter plot
#rgl.bbox(color=c("#333377","black"), emission="#333377",specular="#3333FF", shininess=5, alpha=0.5 ) 
#rgl.lines(c(min(x), max(x)), c(0, 0), c(0, 0), color = "black")
#rgl.lines(c(0, 0), c(min(y),max(y)), c(0, 0), color = "red")
#rgl.lines(c(0, 0), c(0, 0), c(min(z),max(z)), color = "green")
#rgl.planes(a = c(1,0,0), b = c(0,1,0), c = c(0,0,1))
#rgl.close()

#rgl.open()
#rgl.close()
```



```{r}
library(scatterplot3d)
model.1 <- lm(I ~ A + D, data = out.2.df)

s3d <- scatterplot3d(out.2.df[,c("I","A","D")],angle = 90, highlight.3d = TRUE)
s3d$plane3d(model.1)

```



```{r}
s3d.2 <- scatterplot3d(out.2.df[,c("I","A","D")],angle = 180, highlight.3d = FALSE, color = "blue", pch = 16)
s3d.2$plane3d(model.1)
```
```{r}
model.test <- lm(I ~ A + D, data = out.test)
s3d.2 <- scatterplot3d(out.test[,c("I","A","D")],angle = 125, highlight.3d = FALSE, color = "blue", pch = 16)
s3d.2$plane3d(model.1)
#180
#125
```



```{r}
out.plot <- as.data.frame(ode(y = state.gallup, times = seq(0,428,1), func = IAD, parms = parameters.2))

plot(x = 1,                 
     xlab = "Time (Semi-Weekly)", 
     ylab = "Percent of Population",
     xlim = c(0, 400), 
     ylim = c(0, 1),
     main = "Real Gallup Data",
     type = "n")
grid()
points(x = gallup.trump.approval$time, y = gallup.trump.approval$indifferent, col = "blue",pch = 20)
points(x = gallup.trump.approval$time, y = gallup.trump.approval$agree, col = "red",pch = 20)
points(x = gallup.trump.approval$time, y = gallup.trump.approval$disagree, col = "green",pch = 20)
points(x= out.plot$time, y = out.plot$A, col = "orange", pch = 1, cex = 0.2)
points(x= out.plot$time, y = out.plot$I, col = "orange", pch = 1, cex = 0.2)
points(x= out.plot$time, y = out.plot$D, col = "orange", pch = 1, cex = 0.2)

```



```{r}
library(ggplot2)
ggplot() +
geom_point(x = gallup.trump.approval$time, y = gallup.trump.approval$indifferent, col = "blue") +
geom_point(x = gallup.trump.approval$time, y = gallup.trump.approval$agree, col = "red") +
geom_point(x = gallup.trump.approval$time, y = gallup.trump.approval$disagree, col = "green")
```

```{r}
i0 <- tail$I
a0 <- tail$A
d0 <- tail$D

(gamma1*a0 + gamma2 * d0)/(beta1*a0 + beta2 * d0)

beta1*gamma1 + beta1*alpha1*a0 - beta1*alpha2*a0 + beta2*alpha1*d0-beta2*alpha2*d0-beta2*gamma1


(beta2*gamma1 - beta2 * gamma2 + beta2 * gamma2 * d0 - beta2*alpha2 * d0) / (beta1 * alpha1 - beta2*alpha2)
```

```{r}
time.series.4 <- plot_ly(gallup.trump.approval, x = gallup.trump.approval$time, type = "scatter", mode = "markers")
time.series.4 <- time.series.4 %>% add_trace(y = gallup.trump.approval$indifferent , name = "IndifferentR",marker = list(size = 5, color = "blue"))
time.series.4 <- time.series.4 %>% add_trace(y = gallup.trump.approval$agree , name = "AgreeR",marker = list(size = 5, color = "orange"))
time.series.4 <- time.series.4 %>% add_trace(y = gallup.trump.approval$disagree, name = "DisagreeR", marker = list(size = 5, color = "green"))
time.series.4 <- time.series.4 %>% add_trace(y = out.plot$I, name = "Indifferent", marker = list(size = 5, color = "blue"))
time.series.4 <- time.series.4 %>% add_trace(y = out.plot$A, name = "Agree", marker = list(size = 5, color = "orange"))
time.series.4 <- time.series.4 %>% add_trace(y = out.plot$D, name = "Disagree", marker = list(size = 5, color = "green"))
time.series.4 <- time.series.4 %>% layout(title = "Model and the Real Data", font = t, xaxis = x.title, yaxis = y.title, legend= c(l, list(title=list(text='<b> Populations </b>'))))
time.series.4

#, y = gallup.trump.approval$indifferent, name = "IndifferentR"
```



